Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-04-01 W13report.tex
peak probabilities

>>>>

We can model source free image (i.e.\ with a background described by a
Gaussian process) using the statistics of Gaussian random fields
(Kaiser 2004). For an image with Gaussian noise convolved with a
Gaussian PSF with width $\sigma_g$ the density of peaks above a given
detection threshold, $\nu$ is given by 
\begin{equation}
n(>\nu) = \frac{1}{2^{5/2}\pi^{3/2}\sigma_g^{2}} \nu e^{-\nu^2 /2} 
\end{equation}
 To estimate the number of random
positive detections for a given image we must normalize this density
by the total number of realizations of the PSF within the image, i.e.,
\begin{equation}
N_{total}(>\nu) = n(\nu)*nrow*ncol/PSF_{FWHM}^2
\end{equation}
where nrow and ncol are the number of rows and columns in an images
and $PSF_{FWHM}$ is the FWHM of the PSF.

Figure~\ref{fig:peaks} shows good agreement in a comparison of this
model to a Monte-Carlo simulation for thresholds $4<\nu<6$ for a
4000x4072 pixel image with 0.88 arcsec seeing. The variance on these
measures is shown in Figure XXX
\begin{figure}
\includegraphics[width=0.5\textwidth,
height=0.25\textwidth]{figures/peaks.eps} 
\caption{A comparison of the predicted number of random peaks (solid
  line) detected in an image, as a function of significance, with
  those derived from a Monte-Carlo realization of a Gaussian noise
  image (solid points).}
\label{fig:peaks}
\end{figure}
